How does color influence our political conversations?

### 2023-07-09 chapter_3/src/slides/slides.qmd
make some extra additions to slides

@@

@@

# Sensitivity of conclusions to sample size, research design, and modeling strategies {.appendix}

@@

## Fitting the models on the simulated data

@@

### Model 1

@@

### Model 2

@@

### Model 2 (alternate)

@@

## Performance

@@

### Model 1
```{r}
#| label: fig-true-positive-study-1-model-1
#| fig-cap: True positive rate from simulations - Model 1
#| layout-nrow: 1
plot_study_1_model_1 <- true_positive_plot(data_frame = df_fitted_samples_model_1)
plot_study_1_model_1[[1]]
```

>>>>

- Prime condition: political attitudes questionnaire before treatment vs. after
- Person wearing shirt might be White Female (but would like some feedback on this)

@@

- Congruency is whether or not policy attitudes after image matches with presumed partisanship from color of shirt
  - Policy positions will be on: Support for Gun Control, whether pro-choice or pro-life, support for Universal Basic Income

## Outcomes

- $H_1$: What color shirt was your political discussion partner wearing?
- $H_2$ \& $H_3$: To what extent are you willing to have a conversation with this person? (5-item response)

@@

# Appendix {.appendix}

## Sensitivity of conclusions to sample size, research design, and modeling strategies {.appendix}

@@

### Fitting the models on the simulated data

@@

#### Model 1

@@

#### Model 2

@@

#### Model 2 (alternate)

@@

### Performance

@@

#### Model 1
```{r}
#| label: fig-true-positive-study-1-model-1
#| fig-cap: True positive rate from simulations - Model 1
#| layout-nrow: 1
plot_study_1_model_1 <- true_positive_plot(data_frame = df_fitted_samples_model_1)
plot_study_1_model_1[[1]]
```
